Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-16 paper/v1.0/sections/1_introduction.tex
Add introduction paper

Interactions between light and matter have dragged research attention in the fields of optoelectronics, sensing, energy harvesting, quantum computing, bio-information, and in many branches of recent technologies. For many years, the foremost aims for examing the characteristics of dressed fermion systems were focused on the different types of atomic and molecular arrangements. These researches of extreme electron-light engagements introduced an astonishing scope of twentieth-century physics namely quantum optic physics.

On the other hand, in nanostructures that are applicable in electronic devices, the investigations with the help of quantum optic were centered on polaritonic and exciton influences on nanostructures and material characteristics of dressed electrons in two-dimensional(2D) materials and quantum wires. When considering the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.

Therefore, transport properties of nanostructures exposed to a high intensity periodic electromagnetic fields have been explored theoretically in this study. The dressing field is analyzed non perturbatively using the Floquet theory whilst the probing field is examined perturbatively by applying the linear response method using the Kubo formula. The general Floquet-Drude conductivity has been derived in a fully closed analytical form in most recent research [1,2], introducing a novel type of Green’s functions namely four-times Green’s functions.
As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nanostructures by an intense dressing field. From an empirical sense, this study applies directly to various nanostructures illuminated by a high-intensity electromagnetic field.
In this research we have developed a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field and that will enable efficient manipulation of transport characteristics in nanoscale electronic devices.

When a stationary magentic field applied perpendicularly across the surface of 2DEG systems, the orbital motion of electrons becomes completely quantized and the energy spectrium becomes discrete by creating Landau levels. Such a singular system known as a quantum Hall system and in this study we explictly calculate the diagonal ($\sigma_{xx},\sigma_{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems.

Although there are already exist a number of adavanced theories devoted to the calculation of conductivity tensor elements in a quantum Hall systems [3-5], they have not been applied to the optically manipulation the magneto-electric properties of the quantum Hall systems. However K. Dini et al. [6] have recently investigated the one directional conductivity behaviour of dressed quantum Hall systems, they have not used the state of art model to describe the conductivity in a quantum Hall system. In their study they used the conductivity models from T. Ando et al. [3,4] and as mentioned in A. Endo et al. investigation [5] those models are far less accurate representation of the experimantally observed Landau levels because they present a semi-elliptical broadening.

In this study we develop a genralized mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [1,2]. In addition, we demonstrate that our generalized model is agreed with the state of art conductivity model [5] for specalized quantum Hall system which has been considered without the external dressing field.  Therefore this theory describes that the dressing field can be used as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-optoelectonic devices.

>>>>

Manipulating physical systems as a consequence of light engagements introduced an astonishing scope of twentieth-century physics namely quantum optics [15].
Quantum optics have dragged research attention in the disciplines of optoelectronics [1,2,3], sensing [4,5,6], energy harvesting [7,8], quantum computing [9,10,11], bio-information [12,13], and abundant affiliates of recent technologies [14]. 
The studies on quantum optics of nanostructures were centered on metamaterials [28,34], quantum plasmonic effects [27,33], lasers and amplifiers [29,30], quantum cavity physics [31,32]. However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding the transport characteristics [16-24]. 
The significance of describing fundamental mechanisms taking place in charge transport is that they will pave the way to invent new nanoelectronic devices and optimize their performance [35].
Among these works, most studies have considered the driving field as a perturbative field [18,20] that is not applicable for systems under high-intensity illumination [24,25]. When the external electromagnetic field account with a perturbation method and it gets high intensive, the number of higher-order interaction terms need to be consider gets increase. Then a more accurate and powerful concept need to be adopt and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) [18,36,37]. On account of the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.
A theoretical analyses of the transport properties of dressed fermions systems were recently reported in Ref. [22,18,24] where a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form in Ref. [24], introducing a novel type of Green’s functions namely four-times Green’s functions. As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nano-structures by an intense dressing field.

On the other hand, quantum Hall effect [39] observed for two-dimentional fermions systems at low temperatures under strong staionary magnetic field manifest remarkable magneto-transport behaviours and transport properties of these systems attracted many researches attention in experimentally [40,41,42] and theoretically [43,44,45,46,47]. Akira Endo et al. [47] previously presented calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoritical calculations are well-suited with the experimental observations while other former studies [46] yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results [47].

In contrst more fascinating transport phenomena can be achieved by creating a quantum Hall system using a stationary magnetic field and simltaneously applying a dressing field.
Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems [43,47,48], they have not been utilized to describe the optical manipulation of the transport properties of the quantum Hall systems.
Furthermore K. Dini et al. [23] have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems and they have not adopted the state of art model to describe the conductivity in a quantum Hall system. In their study, they used the conductivity models from T. Ando et al. [43,48] and as mentioned in A. Endo et al. work [47] those models yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results.

In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantised and the energy spectrum becomes discrete by creating Landau levels [49].
Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the diagonal ($\sigma_{xx},\sigma_{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalised mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [24].
Finaly we demonstrate that our generalised model is agreed with the state of art conductivity model [47] already developed for specialised quantum Hall systems that have been considered without the external dressing field.  
Furthermore the mechanism of optical manipulation can be used as a tool to utilise transport properties in various two-dimentional nano-structures which serve as a basis for nano-electronic devices and we belive that our theoritical analysis and visual depictions of results can be used to undestand the basic structure and optimize the performance of optical manipulation of trasport propeties in a two-dimentional quantum Hall system.
